\documentclass[sigconf,nonacm]{acmart}

% links
\usepackage{hyperref}
% foreach macro
\usepackage{pgffor}
% file contents utilities
\usepackage{filecontents}
\usepackage{array}
\usepackage{subcaption}
\usepackage{graphicx}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\newcolumntype{L}{>{\centering\arraybackslash}m{3cm}}

\begin{document}

\title{ThisEventDidNotHappen}
\subtitle{Data/Science/Society \\ Student ID: ge38rak \\ Winter Term 2020/2021}

\author{Adrian David Castro Tenemaya}
\email{adrian.castro@tum.de}
\affiliation{%
  \institution{Technische Universit{\"a}t M{\"u}nchen}
}

\begin{abstract}
  Even before internet became popular, fake news and people disguising themselves as someone else existed all over the world. From gossip spreading, to the use of fake passports, going ``off the grid'' and living in the woods. People always tried to get away from something they were, or something they have done, or tried to change the course of history by telling lies.

  The effect however, has been ever so slow as the fastest mean of communication available at the time.

  Communication at the speed of light is a game changer. In seconds, people across the globe know about fake cults, conspiracy theories, and much, much more.
  Today, a \textit{tweet} alone can alter the course of history, save lives, or even take them away.

  Today, people can be whoever they want online. A waitress, a business owner, a monk, or a dog. On the internet, no one knows you are a dog.

  Today, people can change their faces on the internet, or create entirely new ones, never before seen.

  Today, more than ever, pen is mightier, and faster, than the sword.
\end{abstract}

\maketitle

\input{00_Introduction/00_Introduction.tex}
\input{01_AllYourData/01_AllYourData.tex}
\input{02_RiseOfFakeIdentities/02_RiseOfFakeIdentities.tex}
\input{03_FakeNews/03_FakeNews.tex}
\input{04_GANs/04_GANs.tex}

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}
